Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-09-27 analysis/paper_draft3.Rmd
Update paper_draft3.Rmd
Updated notation, sex/gender, and some comments. Will show in meeting on Friday

\begin{equation}  
L(b|\delta) = \prod_{i=1}^{n_i} \prod_{j=1}^{n_j}(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}})^{\delta_{ij}} (\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}})^{1-\delta_{ij}}
\label{eq:model3}
\end{equation} where $n_{i}$ is the total number of jury selections (trials); and $n_j$ is the total number of peremptory strikes.

@@

\begin{equation}  
\pi(b|\delta_0,\alpha_0) \propto L(b|\delta_0)^{\alpha_0}\pi_0(b)
\label{eq:powerprior}
\end{equation} where $0 \le \alpha_0 \le 1$ is the parameter controlling the weight of the historical information; $\delta_0$ is the observed historical data; $L(b|\delta_0)$ is the likelihood function of $b$ given the historical data; and $\pi_0(b)$ is the initial prior before the historical data is observed.

@@

\begin{equation}
  P(b|\delta,\delta_0) \propto L(b|\delta)(L(b|\delta_0))^{\alpha_0}\exp(-\frac{(b-\mu)^2}{2\sigma^2})
  \label{eq:model4}
\end{equation} where

@@

In the default setting, the pull-down menus for prosecutor and defense are set to "None". As a result, the app ignores any historical strike data and estimates the posterior distributions of the bias parameter for prosecutor and defense based only on the strike tally data and the initial prior ($b \sim N(0,2)$).

>>>>

\begin{equation}  
L(b|\delta) = \prod_{i=1}^{n_i} \prod_{j=1}^{n_j}(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}})^{\delta_{ij}} (\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}})^{1-\delta_{ij}}
\label{eq:model3}
\end{equation} where $n_{i}$ is the total number of jury selections (trials), $n_j$ is the total number of peremptory strikes, and $\delta=(\delta_{11},\dots,\delta_{12},\dots,\delta_{{n_i}{n_j}})$

@@

\begin{equation}  
\pi(b|\delta_0,\alpha_0) \propto L(b|\delta_0)^{\alpha_0}\pi_0(b)
\label{eq:powerprior}
\end{equation} where $0 \le \alpha_0 \le 1$ is the parameter controlling the weight of the historical information; $\delta_0=(\delta_{011},\dots,\delta_{012},\dots,\delta_{0{n_i}{n_j}})$ is the observed historical data; $L(b|\delta_0)$ is the likelihood function of $b$ given the historical data; and $\pi_0(b)$ is the initial prior before the historical data is observed.

@@

\begin{equation}
  \pi(b|\delta,\delta_0) \propto L(b|\delta)(L(b|\delta_0))^{\alpha_0}\exp(-\frac{(b-\mu)^2}{2\sigma^2})
  \label{eq:model4}
\end{equation} where

@@

In the default setting, the pull-down menus for prosecutor and defense are set to "None". As a result, the app ignores any historical strike data and estimates the posterior distributions of the bias parameter for prosecutor and defense based only on the strike tally data and the initial prior ($b \sim N(0,2)$). Historical data will be included if the name(s) of a prosection or defense attorney are selected from the pull-down menu. Subsequently, the amount of historical data to be borrowed can be selected by the choice of $\alpha$.
